=enter title here=

### 2019-06-11 doc/paper/body.tex
starting to work on james submission for pierre

While Eq. (\ref{medlyn}) can be used in PM (Eq. (1)), it will make
analytical work with the function intractable because GPP is
functionally related to ET itself. Additionally, a perturbation to VPD
should induce a physiological plant response that will alter GPP and
cause an indirect change in stomatal conductance, in addition to the
direct effect of VPD in Eq. (\ref{medlyn}). Therefore, in order to
derive the full plant response of ET to VPD, we must account for the
functional relationship between GPP, ET, and VPD, and its effect on
stomatal conductance. We can use aforementioned semi-empirical results
of \citet{Zhou_2015}, which were inspired optimal photosynthesis
theory, as a tool to approach this problem. \citet{Zhou_2015}, showed
that underlying Water Use Efficiency (uWUE):

@@

Additionally, the sensitivity of ET response to plant parameters
highlights the importance of understanding and developing stomatal
conductance models and parameters for the ecosystem scale. In
particular, why and how g$_1$ behavior at the leaf scale is not
analogous to the ecosystem scale must be understood. While the
derivation here was explicit about the assumption of a constant g$_1$
term with respect to the VPD perturbation, many sophisticated land
surface models and earth system models employing stomatal conductance
models make similar assumptions about the stationarity of VPD slope
terms \citep{Niu_2011, Franks_2017, Rogers_2017, Lawrence_2019}. Many
models will assume a constant VPD slope term (e.g. g$_1$) term within
a given plant functional type, and research derived from these models
often does not acknowledge limitations of this assumption, or the
difficulty in the literature with quantifying an ecosystem scale slope
parameter \citep{Medlyn_2017}. Given that something so fundamental as
the ET response to VPD varies strongly with g$_1$, we must invest more
in understanding g$_1$'s behavior at the ecosystem scale, and the
efficacy of models using constant slope terms for ecosystem-scale
fluxes. Fortunately, our framework, and the new approach of using
robust ecosystem-scale ratios (uWUE) to remove the implicit dependence
of stomatal conductance on ET, is flexible enough to be applied to any
stomatal conductance model that contains a dependence on GPP.

>>>>

While Eq. (\ref{medlyn}) can be used in PM (Eq. (1)), it will make
analytical work with the function intractable because GPP is
functionally related to ET itself. Additionally, a perturbation to VPD
should induce a physiological plant response that will alter GPP and
cause an indirect change in stomatal conductance, in addition to the
direct effect of VPD in Eq. (\ref{medlyn}). Therefore, in order to
derive the full plant response of ET to VPD, we must account for the
functional relationship between GPP, ET, and VPD, and its effect on
stomatal conductance. We can use aforementioned semi-empirical results
of \citet{Zhou_2015}, which were inspired by optimal photosynthesis
theory, as a tool to approach this problem. \citet{Zhou_2015}, showed
that underlying Water Use Efficiency (uWUE):

@@

Additionally, the sensitivity of ET response to plant parameters
highlights the importance of understanding and developing stomatal
conductance models and parameters for the ecosystem scale. In
particular, why and how g$_1$ behavior at the leaf scale is not
analogous to the ecosystem scale must be understood. While the
derivation here was explicit about the assumption of a constant g$_1$
term with respect to the VPD perturbation, many sophisticated land
surface models and earth system models employing stomatal conductance
models make similar assumptions about the stationarity of VPD slope
terms \citep{Niu_2011, Franks_2017, Rogers_2017, Lawrence_2019}. Many
models will assume a constant VPD slope term (e.g. g$_1$) within
a given plant functional type, and research derived from these models
often does not acknowledge limitations of this assumption, or the
difficulty in the literature with quantifying an ecosystem scale slope
parameter \citep{Medlyn_2017}. Given that something so fundamental as
the ET response to VPD varies strongly with g$_1$, we must invest more
in understanding g$_1$'s behavior at the ecosystem scale, and the
efficacy of models using constant slope terms for ecosystem-scale
fluxes. Fortunately, our framework, and the new approach of using
robust ecosystem-scale ratios (uWUE) to remove the implicit dependence
of stomatal conductance on ET, is flexible enough to be applied to any
stomatal conductance model that contains a dependence on GPP.
